Real Estate

### 2022-10-25 src/real_estate.Rmd
complied real estate and demographic data

library(googlesheets4)

@@

```{r}
# aggregate yardi data into MSAs by cbsa
MSA_realEstate_data <- city_realEstate_data %>%

@@

```{r}
# calculate rent to income ratio

>>>>

library(tidyverse)
library(janitor)
library(googlesheets4)

@@

```{r}
# aggregate yardi data into MSAs by cbsa
MSA_realEstate_data <- city_realEstate_data %>% 
  clean_names() %>% 
  group_by(cbsa) %>% 
  summarize(avg_rent_2021 = mean(average_rent_2021, na.rm = TRUE),
            avg_rent_2022 = mean(x2022_rent, na.rm = TRUE),
            avg_occupancy_21 = mean(percent_occupancy_2021, na.rm = TRUE))

@@

```{r}
# combine real estate and demographic data by cbsa
MSA_demo_data <- MSA_demo_data %>% 
  left_join(MSA_realEstate_data)
```

```{r}
# calculate rent to income ratio
compliedMSA_realEstate <- MSA_demo_data %>% 
  mutate(income_to_rent = median_income_USD_2021/avg_rent_2021)
